Challenges in Developing Great MCQMC Software

### 2022-07-24 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and  friends \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Please join us Tuesday, July 19, at 12:45 PM for lunch at Bella Casa \\ to discuss the future of MCQMC software \\[2ex]
	Thanks to the organizers as we meet again in person\\
	Slides at  \href{https://speakerdeck.com/fjhickernell/challenges-of-developing-mcqmc-software}%
	{\nolinkurl{speakerdeck.com/fjhickernell/challenges-of-developing-mcqmc-software}}
}
\event{MCQMC 2022, Linz}
\date[]{July 18, 2022}

@@

\begin{description}[\labelwidth=5ex,\leftmargin=10ex]
	%\setlength{\labelwidth}{5ex}

@@

    \item<2-> Recommendations
    \begin{itemize}
    \item Contribute your new idea as a \alert{demo} in your favorite library
    \item If your contribution is substantial, add as a \alert{feature} to other libraries
    \item Move basic features of your library to \alert{larger} library
    \item Write wrappers or demos to \alert{connect} other libraries to your library

>>>>

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and  friends \\
	partially supported by SigOpt (Intel) and an Illinois  Tech alum\\[2ex]
	Join us Tuesday, July 19, at 12:45 PM for lunch at Bella Casa \\ to discuss the future of MCQMC software \\[2ex]
	Thanks to the organizers as we meet again in person\\
	Slides at  \href{https://speakerdeck.com/fjhickernell/challenges-of-developing-mcqmc-software}%
	{\nolinkurl{speakerdeck.com/fjhickernell/challenges-of-developing-mcqmc-software}}
}
\event{MCQMC 2022, Linz}
\date[]{July 18, 2022}

@@

\begin{description}[alabel]
	%\setlength{\labelwidth}{5ex}

@@

    \item<2-> Recommendations if you want to contribute software
    \begin{itemize}
    \item Realize your new idea as a \alert{demo} in your favorite library
    \item Add a significant idea as a \alert{feature} to other libraries
    \item Move basic features of your library to \alert{larger} library
    \item Write wrappers or demos to \alert{connect} other libraries to your library
